%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  {\Huge \scshape Nimai Patel} \\ \vspace{1pt}
  State College, Pennsylvania \\ \vspace{1pt}
  \href{https://linkedin.com/in/nimaipatel/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/nimaipatel}} ~
  \href{https://github.com/nimaipatel}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/nimaipatel}} ~
  \href{https://nimaipatel.github.io}{\raisebox{-0.2\height}\faGlobe\ \underline{nimaipatel.github.io}} \\ \vspace{5pt}
  \small \raisebox{-0.1\height}\faPhone\ +1 (267) 461-8832 ~ \href{mailto:nimai.m.patel@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{nimai.m.patel@gmail.com}} ~
  \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{The Pennsylvania State University}{August 2023 -- Present}
{Master of Science in Computer Science and Engineering}{State College, PA}
\resumeSubheading
{University of Mumbai}{August 2019 -- May 2023}
{Bachelor of Technology in Information Technology {\textbf{CGPA: 9.22/10}}}{Mumbai, India}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Meshnet Electronics}{March 2022 -- March 2023}
{Embeded Systems Engineer}{Mumbai, India}
\resumeItemListStart
\resumeItem{Spearheaded the implementation of over-the-air updates,
  NTP time synchronization, remote and serial configuration of SOCs, and
  seamless Modbus communication using C++ and C on the ESP32
  microcontroller.}

\resumeItem{Orchestrated the design of all components with a
  focus on minimal coupling, ensuring seamless integration
  into any project with a significant reduction in development time.}

\resumeItem{Led comprehensive testing initiatives, including conducting
  20+ range tests, achieving 98\% accuracy in sensor calibration, and
  conducting OTA reliability testing that led to a 40\% increase in
  system stability.}
\resumeItemListEnd

\resumeSubheading
{Tata Advanced Systems Limited}{July 2022 -- April 2023}
{Cybersecurity Project Intern}{Mumbai, India}
\resumeItemListStart
\resumeItem{Engineered a robust SOC for TASL by integrating
  Wazuh, Suricata, and Graylog through the application of Python, Unix
  scripting, and PowerShell scripting, resulting in 40\% faster incident
  response times.}

\resumeItem{Customized attack vectors for IT infrastructure using
  Caldera, delivering comprehensive security coverage, and generated
  reports with explanatory graphs and tables automatically using Python scripts.}

\resumeItem{Attained 100\% automation for system deployment using
  Python and shell scripting which resulted in a remarkable 75\%
  reduction in deployment time, enhancing overall security and
  operational efficiency.}
\resumeItemListEnd

% \resumeSubheading
% {The Pennsylvania State University}{August 2023 -- Present}
% {Learning Assistant for CMPSC 311}{State College, PA}
% \resumeItemListStart
% \resumeItem{Gradute Leaning Assistant for CMPSC 311 -- Introduction to System Programming}
% \resumeItem{Conducting effective office hours, addressing students' doubts regarding C and Unix programming, 
%   solving environment setup-related issues, and grading papers and assignments}
% \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Rideshare -- Decentralized Ride-hailing System
      {\href{https://ieeexplore.ieee.org/document/10037296}{\
          \underline{\textsuperscript{[DOI]}}}}}}{}
\resumeItemListStart
\resumeItem{Used the Ethereum blockchain and Interplanetary File
  System (IPFS) to decentralize cab bookings, resulting in an almost
  100\% reduction in middlemen involvement, potentially enhancing
  efficiency and cost-effectiveness in the real world.}
\resumeItem{Developed a user-friendly front-end using Flutter and
  Dart, ensuring an intuitive experience for users. and conducted
  rigorous testing to guarantee the platform's reliability and user
  satisfaction.}
\resumeItem{Crafted smart contracts in Solidity to facilitate
  secure and transparent transactions and Implemented IPFS server
  code in Node.js, to enhance data storage and retrieval efficiency.}
\resumeItemListEnd
\vspace{-13pt}
\resumeProjectHeading
{\textbf{Open Source Projects \& Contributions}}{}
\resumeItemListStart
\resumeItem{Developed {\href{https://www.github.com/nimaipatel/brn}{\underline{brn}}{}}, a one of its kind C-based sys-admin utility that can be used to bulk rename files easily. It handles cycles in name changes gracefully using the renameat2 system call on Linux.}
\resumeItem{Contributed to various Lua-based plugins for the Neovim text editor.}
\resumeItem{Designed patches for {\href{https://www.github.com/nimaipatel/st}{\underline{X11 terminal emulator}}} and \href{https://www.github.com/nimaipatel/dwm}{\underline{window manager}} that added features such as live config reloading using UNIX signals.}
\resumeItemListEnd
\vspace{-13pt}
\resumeProjectHeading
{\textbf{Web Development Portfolio}}{}
\resumeItemListStart
\resumeItem{Developed a user-friendly web application enabling students to request train pass concessions and generate leaving certificates through the college's portal.}
\resumeItem{Collaborated with a team to create \underline{\href{https://www.github.com/nimaipatel/findit}{FindIt}} a robust Lost \& Found management tool, as part of our submission to the CSI Hackathon. The system efficiently helps users track and retrieve their lost items.}
\resumeItem{Co-engineered \underline{\href{https://www.github.com/stack-review}{StackReview}} alongside my team for OAuth's 2020 Hackathon. The platform facilitates efficient code reviews, fostering collaboration among developers and ensuring code quality.}
\resumeItemListEnd
\vspace{-13pt}
\resumeSubHeadingListEnd
\vspace{-2pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Languages}{: C, C++, Python, Rust, JavaScript, SQL, HTML, CSS, {\LaTeX}, Bash, PowerShell, Lua} \\
                \textbf{Web Technologies}{: React, NodeJS, AWS, Firebase, MongoDB, Flutter, BootStrap, WordPress, Tailwind CSS} \\
                \textbf{Data Science}{: Tableau, Pandas, Numpy, SciPy, MatplotLib} \\
                \textbf{Embeded Systems}{: ESP32, IDF, Arduino}
                \hspace{1em}
                \textbf{Blockchain Development}{: Solidity, Ganache, Truffle} \\
          }}
\end{itemize}
\vspace{-16pt}

\end{document}